Evolution of a conspicuous dynamic visual signal in an introduced chameleon

### 2021-05-05 ms.Rmd
Update to methods

Chromatic and achromatic contrast from visual models, measured in just noticable differences (JNDs), were analysed using linear mixed effects models in R using the `lme4` package (). Across the different contexts (i.e., social contexts, predation and background environments), chromatic and acromatic contrasts were analysed in seperate models as response variables. For analyses involving social context, we included z-transformed snout-vent length (SVL), population of origin, and their interaction as fixed effects. For models involving predatory contexts and visual systems, we included the predator type (i.e, snake or snake), population of origin and their interaction as fixed effects. Finally, to test local adaptation, we used only chameleons from Hawaii and tested the extent to which chromatic and achromatic contrast varied depending on whether Hawaiian signals were obersved on a native Kenyan background or their current introduced habitat background in Hawaii. Model interactions were first tesed using a Type III sum of squares ANOVA with a Saitterwaite degrees of freedom correction, and if found to be non-significant (p > 0.1) we dropped the interaction and fit a main effects model. For all individuals, we measured signals for multiple body regions, each of which were contratsed between multiple background measurements (i.e., top and bottoms of two leaves and two stems). For our main analyses we average estimates across these body regions and background environments given that in many cases body regions showed remarkably similar effects (see Supplementary Results). Deriving multiple contrats for each individual body region and background resulted in a substantial number of comparisons, each of which were not completely indpeendent of each other. To ensure that non-indpendence of data did not impact our inferences we used a Robust Variance Estimator (RVE) on our final model to correct standard errors for within-individual non-independence. In all cases, our results and conclusions were not impacted (see supplmentary code).

>>>>

Chromatic and achromatic contrast from visual models, measured in just noticable differences (JNDs), were analysed using linear mixed effects models in R using the `lme4` package (). Across the different contexts (i.e., social contexts, predation and background environments), chromatic and acromatic contrasts were analysed in seperate models as response variables. For analyses involving social context, we included z-transformed snout-vent length (SVL), population of origin, and their interaction as fixed effects. For models involving predatory contexts and visual systems, we included the predator type (i.e, snake or snake), population of origin and their interaction as fixed effects. Finally, to test local adaptation, we used only chameleons from Hawaii and tested the extent to which chromatic and achromatic contrast varied depending on whether Hawaiian signals were obersved on a native Kenyan background or their current introduced habitat background in Hawaii. Model interactions were first tested using Wald tests using robust variance estimators and a Saitterwaite degrees of freedom correction. If found to be non-significant (p > 0.1) we dropped the interaction and fit a main effects model. We then tested the significance of the main effect of 'Population', 'Predator' or 'Background' (depending on the model) using Wald tests with robust variance estimators and a Saitterwaite degrees of freedom correction. For all individuals, we measured signals for multiple body regions, each of which were contratsed between multiple background measurements (i.e., top and bottoms of two leaves and two stems). For our main analyses we average estimates across these body regions and background environments given that in many cases body regions showed remarkably similar effects (see Supplementary Results). Deriving multiple contrats for each individual body region and background resulted in a substantial number of comparisons, each of which were not completely indpeendent of each other. To ensure that non-indpendence of data did not impact our inferences we used a Robust Variance Estimator (RVE) on our final model to correct standard errors for within-individual non-independence. In all cases, our results and conclusions were not impacted (see supplmentary code).
